Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-09-30 ms/SI.rmd
Use explicit cache
called canopy_cache

# Load analysis results
loadd(trait_data_for_si)
loadd(climate_ancova_results)
loadd(phylosig_binary_traits_strict)
loadd(correlated_evo_test_strict)
loadd(best_fit_div_models_moran)
loadd(func_comm_struc_combined)

>>>>

# Load analysis results
loadd(trait_data_for_si, cache = canopy_cache)
loadd(climate_ancova_results, cache = canopy_cache)
loadd(phylosig_binary_traits_strict, cache = canopy_cache)
loadd(correlated_evo_test_strict, cache = canopy_cache)
loadd(best_fit_div_models_moran, cache = canopy_cache)
loadd(func_comm_struc_combined, cache = canopy_cache)

### 2019-09-30 ms/manuscript.Rmd
Use explicit cache
called canopy_cache

# Load analysis results
loadd(best_fit_div_models)
loadd(climate_ancova_results)
loadd(climate_plot)
loadd(climate_select)
loadd(combined_comm_div_plots)
loadd(combined_cwm_plots)
loadd(comm)
loadd(correlated_evo_test)
loadd(correlated_evo_test_gemmae)
loadd(daily_mean_climate)
loadd(div_el_model_summaries)
loadd(div_t_test_results)
loadd(div_metrics_all)
loadd(fern_traits)
loadd(importance_heatmap)
loadd(pca_plot)
loadd(pca_results)
loadd(phy)
loadd(phylosig_binary_traits)
loadd(phylosig_cont_traits)
loadd(pic_results)
loadd(species_list)
loadd(traits_with_tree)
```

>>>>

# Load analysis results
loadd(list = c(
  "best_fit_div_models",
  "climate_ancova_results",
  "climate_plot",
  "climate_select",
  "combined_comm_div_plots",
  "combined_cwm_plots",
  "comm",
  "correlated_evo_test",
  "correlated_evo_test_gemmae",
  "daily_mean_climate",
  "div_el_model_summaries",
  "div_t_test_results",
  "div_metrics_all",
  "fern_traits",
  "importance_heatmap",
  "pca_plot",
  "pca_results",
  "phy",
  "phylosig_binary_traits",
  "phylosig_cont_traits",
  "pic_results",
  "species_list",
  "traits_with_tree"),
  cache = canopy_cache)
```
